### 2020-09-08 images/flow_noeq_basic.tex
new presentation

  \node (sample)  [screen, join]  {Screen random documents};
  \node (model) [computer, join, left=of sample]  {Train model,\\ predict relevance};
  \node (screenrel)  [screen, below of =sample]  {Screen most \\ relevant documents};
  \node (stopscreen) [decision, join] {Irrelevant?};

  \node (screenr2) [screen, join]  {Screen random documents};

  \node (recall) [decision, join] {Recall $>$ threshold?};

  \node (reldocs) [multidoc, below of=recall, xshift=20mm, yshift=-8mm]  {Relevant documents};
  \node (irreldocs) [multidoc, fill=blue!5, below of=recall, xshift=-20mm, yshift=-8mm]  {Irrelevant documents};
  %\node

@@

  \node [coord, left=of recall, xshift=-45mm] (c3)  {}; %\cmark{1}

@@

  \path (recall.west) to node [very near start, yshift=1em] {$n$} (c3);

 %\draw [o->,norm] (recall.west) -- (c3) |-  (c2) -- (model.north);
 \draw [o->,norm] (recall.west) -- (c3) |-  (screenr2.west);

 \draw [o->,norm] (recall.south) -- (reldocs);
 \draw [o->,norm] (recall.south) -- (irreldocs);

>>>>

  \node (sample)  [screen, join]  {Screen random documents};
  \node (model) [computer, join, left=of sample]  {Train model,\\ predict relevance};
  \node (screenrel)  [screen, below of =sample]  {Screen most \\ relevant documents};
  \node (stopscreen) [decision, join] {Recall $\geq$ target?};

  \node (reldocs) [multidoc, below of=stopscreen, xshift=20mm, yshift=-8mm]  {Relevant documents};
  \node (irreldocs) [multidoc, fill=blue!5, below of=stopscreen, xshift=-20mm, yshift=-8mm]  {Irrelevant documents};
  %\node

@@

@@

 %\draw [o->,norm] (recall.west) -- (c3) |-  (c2) -- (model.north);
% \draw [o->,norm] (recall.west) -- (c3) |-  (screenr2.west);

 \draw [o->,norm] (stopscreen.south) -- (reldocs);
 \draw [o->,norm] (stopscreen.south) -- (irreldocs);
